---
title: "Homework 1"
author: "Noah Foilb"
date: "9/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Load Dataset in from source & libraries
```{r}
source("http://www.openintro.org/stat/data/present.R") # The database
source("http://www.openintro.org/stat/data/arbuthnot.R")
library(ggplot2)
library(dplyr)
```

#1 What years are included in this dataset? What are the dimensions of the data frame and what are the column names
```{r}
# Year ranges from 1940 - 2002
min(present$year)
max(present$year)

# Dimensions are 63 rows and 3 columns
dim(present)

# The column names are year, boys, girls
names(present)
```


#2 Compare the two datasets
```{r}
arbuthnot$boys + arbuthnot$girls
```
```{r}
present$boys + present$girls
```
```{r}
# I took each dataset and summed up the amount of total population each year recorded and the Present dataset has a much larger number of records. 
```


#3 Make a plot that displays the boy-to-girl ratio for every year in the data set. What do you see? Does Arbuthnot’s observation about boys being born in greater proportion than girls hold up in the U.S.? Include the plot in your response.   
```{r}
GB <- present$boys/present$girls
ggplot(present, aes(x = year, y = GB))+ geom_point(colour="blue")

# As you can see the ratio has decreased over time

present$boys > present$girls

# Arbuthnots obersavtion holds up as well!
```


# 4
```{r}
present %>%
  mutate(Total = present$boys + present$girls) %>% 
  arrange(desc(Total))

# The year with the highest toal population was 1961
```








